Amicus Word Count

### 2021-11-12 data-cleaning/01-shorten-amicus-text.Rmd
footnotes search #1

# data manip
library(tidyverse)
library(tidytext)

@@

# Remove text after "Appendix" or "Footnotes"

@@

>>>>

# data manip
library(tidyverse)
library(tidytext)
library(conText)

@@

# Check isntances of "Appendix" or "Footnotes"

@@

# Remove footnotes instances

Process:

0. Check if "footnotes" is within three words of "omitted" -> in this case, do not remove any text.
1. Ignore instances of "footnotes" in our exceptions:
    * 861810659757"
    * 861821999947 (ignore first instance, second instance is footnotes)
    * 861823138310
    * 861811382099
    * 861820447683
2. If "footnotes" is referenced one time, remove all text after this reference
3. If "footnotes" is mentioned more than once, remove text after the first reference

First, get context around "footnotes"

```{r}
# context function changes brief names to "textN" 
# create this var here so we can map files back
brief_names <- amicus %>% 
  arrange(case,brief) %>% 
  mutate(docname = paste0("text", 1:n())) %>%
  select(brief, id, docname)

# remove punctuation
amicus <- amicus %>% 
  arrange(case, brief) %>% 
  mutate(txt_short_clean = gsub("[^[:alpha:][:space:][:digit:]]", " ", txt_short),
                            txt_short_clean = str_squish(txt_short_clean))

# get context around "footnotes"
footnotes_context <- get_context(x = amicus$txt_short_clean, target = "footnotes", 
                                 window = 5, valuetype = "fixed",
                                 case_insensitive = T, hard_cut = F, verbose = F)
```

Cases where "footnotes" actually references footnotes section, by intuition and some manual inspection:
* footnotes 1
* footnotes counsel of record

```{r}
footnotes_confirmed <- brief_names %>%
  left_join(., footnotes_context, by = "docname") %>%
  select(-target) %>%
  mutate(footnotes_true = ifelse(grepl(" 1 ", context) |
                                   grepl("counsel of record", context),
                                 1, 0)) %>%
  filter(footnotes_true == 1)

footnotes_confirmed %>% distinct(id) %>% nrow()
```

No footnotes:

```{r}
amicus %>% filter(!grepl("footnotes", txt_short)) %>% nrow()
```

Remaining cases: note that this df can have multiple instances of the same case if more than one instance of "footnotes" found.

```{r}
footnotes_tbd <- brief_names %>%
  left_join(., footnotes_context, by = "docname") %>%
  # remove instances of confirmed footnotes (n = 398)
  filter(!(id %in% footnotes_confirmed$id)) %>% 
  # remove instances where "footnotes" not found (n = 270)
  filter(!is.na(context))
```

Save this file for checking:

```{r}
#box_write(footnotes_tbd, file_name = "briefs to check footnotes.xlsx", dir_id = 145990409196)
```
